##R Cheat Sheet

####Table Of Contents
http://www.personality-project.org/R/r.commands.html

-  [Help Commands](#help)
-  [Package Commands](#package)
-  [Inspecting Variables](#input)
-  [Moving Around ](#moving)
-  [Data Manipulation](#data)
-  [Statistics and transformations](#statistics)
-  [Graphics](#graphics)



### <a name="help"></a>Help Commands 

**Find out more about a function**

```{r,echo=FALSE}
# functionName or help(functionName)

?rnorm  
help(rnorm)

```

**Learn about the different ways to use a function**

```{r,echo=FALSE}
#example(functionName)

#example(rnorm) 
```

**Display the arguments of a function**

```{r,echo=FALSE}
#args(functionName)

args(rnorm)

```              

**Search through R's help documentation for a specific term**
```{r,echo=FALSE}
#help.search("your search term")

?rnorm
help(rnorm)
```

### <a name="package"></a> Package Commands

**Install a Package**
```{r,echo=FALSE}
#install.packages("package name")

#install.packages('rnorm')
```

**Find installed packages**
```{r}
   installed.packages()
```


### <a name="input"></a> Inspecting Variables

**Find the Class of a variable**
```{r}
x <- 3
class(x)

```





### <a name="moving"></a> Moving Around Commands
### <a name="data"></a> Data Manipulation Commands
###<a name="statistics"></a> Statistics and Transformations Commands
### <a name="graphics"></a> Graphics Commands

